\textbf{Preprinting Microbiology}

### 2017-02-21 submission/Schloss_PrePrints_mBio_2017.tex
Final rendering prior to submitting preprint

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication. The broad consensus at this point is that
preprints do not constitute prior publication. This consensus is
reflected in the current policies of journals that commonly publish
microbiology research including those published by ASM, the Microbiology
Society, International Society for Microbial Ecology, PLOS, the
\emph{Proceedings of the National Academy of Science}, \emph{Science},
\emph{Nature} and Cell press, which each take a generally permissive
stance towards prior posting of preprints prior to submission.
Considering the relatively fluid nature of many of these policies and
the journals' specific policies, prospective authors should be aware of
the positions taken by the journals where they may eventually submit
their work. Comprehensive lists of journals' attitudes towards preprints
are available online and are regularly updated (9, 10).

\textbf{\emph{Preprints and peer-review.}} The use of preprints for
citations in other scientific reports and grant proposals has been
called into question because preprints upend the traditional peer-review
editorial process (11). It is important to note that the peer-review
process was adapted to the technologies and trends that have evolved
over the past 100 years. The formal peer-review system that most
journals currently use was not developed until the end of the 1800s with
the advent of typewriters and carbon paper (12). Editorial decisions
were typically made by a single person or a committee (i.e.~the
editorial board) who had an expertise that covered the scope of the
journal. As science became more specialized, new journals would form to
support and provide a source of validation to the new specialty. The
growth in science in the mid 1900s resulted in a shift from journals
struggling to find sufficient numbers of manuscript to publish to having
too many manuscripts submitted. It has been argued that the widespread
adoption of decentralized peer-review was due to the increased
specialization and to deal with the large number of manuscript
submissions (13). Peer-review did not achieve widespread use at many
journals, including the \emph{Journal of Bacteriology}, until the 1940s
and 1950s. Thus the ``tradition'' of peer-review is only 70 years old.
Given the rapid advances in communication technology and even greater
specialization within microbiology, it is worth pondering whether the
current scientific publishing system and peer-review system, in
particular, need to continue to adapt with our science.

@@

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. The use of preprints uncouples the communication of the
discovery from the relevance of the discovery, which will come later
based on peer-review, comments from other scientists at meetings or
online, and eventually citations. A growing number of scientific
societies and journals, including ASM view preprints as citable and as
having a legitimate claim to primacy (1, 14--16). Some scientists worry
that with such protection a researcher can make a claim without valid
data to support their claims (3). This is possible; however, it is also
the responsibility of the scientific community to utilize the
peer-review mechanisms that are available to comment on those preprints
pointing out methodological problems or to indicate that they are
speaking beyond the data.

@@

A third concern is what role preprints should have in assessing a
scientist's productivity. Clearly use of publication metrics as an
indicator of a scientist's productivity and impact is a contentious
topic without even discussing the role of preprints. Regardless, given
the propensity for researchers to list manuscripts as being ``in
preparation'' or ``in review'' on an application or curriculum vitae,
listing them instead as preprints that can be reviewed by a committee
would significantly enhance an application and a reviewer's ability to
judge the application. In fact, several funding agencies including the
Wellcome Trust and the UK Medical Research Council encouraging
fellowship applicants to include preprints in their materials;
meanwhile, the NIH is in the process of soliciting input from the
scientific community on their role in grant applications. Others are
mandating that researchers post preprints for all of their work prior to
submitting the work to a journal (17).

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (18). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those who need to cite a report of a brief research communication, a
critique of another publication, or negative results. It is clear that
the adoption of preprints will challenge how scientists interact and
evaluate each other's work. There is great potential to empower
researchers by controlling when a citable piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
study by Afshinnekoo et al. online (19). The study collected and
analyzed metagenomic sequence data from the New York City subway system
and reported finding \emph{Yersinia pestis} and \emph{Bacillus
anthracis}. Because of the focus on these two bioterrorism agents, this
study generated a considerable amount of media attention. On April 25,
2015, Petit et al. (20) posted a preprint to Zenodo demonstrating that
there was no evidence for \emph{B. anthracis} in the dataset. On July
29, 2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (21, 22). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (23) was first
published online. The authors claimed that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (24); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(25, 26). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (27--29).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
reporting numerous cases of image manipulation in peer reviewed studies
(30). Their preprint was posted on April 20, 2016 and published in
\emph{mBio} on June 7, 2016 (31). Instead of using preprints to react to
published papers that have been through peer review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (32) would have been different had
they initially been posted as preprints.

@@

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics I sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, I found that the median number of times an abstract or
PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
568), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, I obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (33). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. I obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, I considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community.

\textbf{\emph{Preprints from an author's perspective.}} Posting research
as a preprint gives an author great control over when their work is made
public. Under the traditional peer-review model, an author may need to
submit and revise their work multiple times to several journals over a
long period before it is finally published. In contrast, an author can
post the preprint at the start of the process for others to consume and
comment on as it works its way through the editorial process. A first
example illustrates the utility of preprints for improving access to
research and the quality of its reporting. In 2014, my research group
posted a preprint to \emph{PeerJ Preprints} describing a method of
sequencing 16S rRNA gene sequences using the Pacific Biosciences
sequencing platform (34). At the same time, they submitted the
manuscript for review at \emph{PeerJ}. While the manuscript was under
review, they received feedback from an academic scientist and from
scientists at Pacific Biosciences that the impact of the results could
be enhanced by using a recently released version of the sequencing
chemistry. Instead of ignoring this feedback and resubmitting the
manuscript to address the reviews, we generated new data and submitted
an updated preprint a year later with a simultaneous submission to
\emph{PeerJ} that incorporated the original reviews as well as the
feedback we received from the academic scientist and Pacific
Biosciences. It was eventually published by \emph{PeerJ} (35, 36). Since
2015, we have continued to post manuscripts as preprints at the same
time as we have submitted manuscripts. Although the feedback to other
manuscripts has not been as helpful as our initial experience, we were
able to sidestep lengthy review processes by immediately making our
results available; in one case our preprint was available 7 months ahead
of the final published version (37, 38). As a second example, this
manuscript was posted to \emph{bioRxiv} as a preprint on
\textbf{February XX, 2017}. I then solicited feedback on the manuscript
using social media. Two weeks later, I incorporated the comments and
posted a revised preprint and submitted the manuscript to \emph{mBio}.
During that time, the abstract was read \textbf{XXXX} times and the PDF
was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. I received
useful feedback from \textbf{XXX} people. Compared to the two or three
scientists that typically review a manuscript, this experience engaged a
much larger and more diverse community than had I foregone the posting
of a preprint. Although there are concerns regarding the quality of the
science posted to a preprint server, I contend that responsible use of
preprints as a part of the scientific process can significantly enhance
the science.

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. Edited peer-reviewed
journals offer and will continue to offer significant added value to a
publication. A scholarly publishing ecosystem in which preprints coexist
with journals will allow authors to gain value from the immediate
communication of their work associated with preprints and also benefit
from the peer-reviewed, professionally edited publication that
publishers can provide. The professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to capture the
innovation opportunities offered by preprints. By adopting
preprint-friendly policies, journals can create an attractive
environment for authors. As discussed above, a growing number of
journals have created mechanisms for authors to directly submit
preprints to their journals. An example is offered by the ASM, which
earlier this year launched a new venture from \emph{mSphere}.
mSphereDirect is a publication track of the journal that capitalizes on
the opportunity offered to couple preprints with rigorous peer-review.
mSphereDirect. actively encourages authors to post their manuscripts as
preprints as part of an author-driven editorial process where an
editorial decision is rendered within five days and publication in
\emph{mSphere} within a month (39). ASM is developing a new platform,
MicroNow, which will help coalesce specific communities within the
microbial sciences, further enhancing the use of preprints as well as
published articles (Stefano Bertuzzi, personal communication). In
addition to integrating preprints into the traditional editorial
process, several professional societies have also explicitly supported
citation of preprints in their other publications and recognize the
priority of preprints in the literature (14--16). These are policies
that empower authors and make specific journals more attractive. Other
practices have great potential to improve the reputation of journals. As
measured above, preprints are able to garner attention on par with
papers published in highly selective microbiology journals. Thus, it is
in a journal's best interest to recruit these preprints to their
journals. Several journals including \emph{PLOS Genetics} and
\emph{Genome Biology} have publicly stated that they scout preprints for
this purpose (40, 41). Preprints can also be viewed as a lost
opportunity to journals. A preprint that garners significant attention
may be ignored when it is finally published, brining little additional
attention to the journal. Going forward, it will be interesting to see
the innovative approaches that publishers develop so that they can
benefit by incorporating preprints into their process and whether
publishers' influence is reduced by the widespread adoption of
preprints.

@@

\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
9. List of academic journals by preprint policy.
\url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.

\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
10. Publisher copyright policies \& self-archiving.
\url{http://www.sherpa.ac.uk/romeo/index.php}.

\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
11. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
articles and why MBoC quickly embraced preprints. Molecular Biology of
the Cell \textbf{27}:3181--3182.
doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.

\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
12. \textbf{Spier R}. 2002. The history of the peer-review process.
Trends in Biotechnology \textbf{20}:357--358.
doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.

\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
13. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
JAMA: The Journal of the American Medical Association \textbf{263}:1323.
doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.

\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
14. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
\textbf{35}:2617--2619.
doi:\url{http://doi.org/10.15252/embj.201670030}.

\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
15. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
\textbf{111}:E01--E02.
doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.

\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
16. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
the life sciences. eLife \textbf{5}.
doi:\url{http://doi.org/10.7554/elife.16931}.

\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
17. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.

\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
18. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.

\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
19. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Geospatial resolution of human
and bacterial diversity with city-scale metagenomics. Cell Systems
\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.

\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
20. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
\textbf{Read TD}. 2015. Searching for anthrax in the New York City
subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.

>>>>

\textbf{\emph{Acceptance of preprints by journals.}} An early
controversy encountered by researchers interested in posting their work
as preprints as a stage in disseminating their research was whether it
constituted prior publication (9). The broad consensus of the
International Committee of Medical Journal Editors and numerous journals
is that preprints do not constitute prior publication (10). This
consensus is reflected in the current policies of journals that commonly
publish microbiology research including those published by ASM, the
Microbiology Society, International Society for Microbial Ecology, PLOS,
the \emph{Proceedings of the National Academy of Science},
\emph{Science}, \emph{Nature}, \emph{Journal of Infectious Diseases},
and Cell press, which each take a generally permissive stance towards
prior posting of preprints prior to submission. Considering the
relatively fluid nature of many of these policies and the journals'
specific policies, prospective authors should be aware of the positions
taken by the journals where they may eventually submit their work.
Comprehensive lists of journals' attitudes towards preprints are
available online and are regularly updated (11, 12).

\textbf{\emph{Preprints and peer-review.}} The use of preprints for
citations in other scientific reports and grant proposals has been
called into question because preprints upend the traditional peer-review
editorial process (13). It is important to note that the peer-review
process was adapted to the technologies and trends that have evolved
over the past 100 years. The formal peer-review system that most
journals currently use was not developed until the end of the 1800s with
the advent of typewriters and carbon paper (14). Editorial decisions
were typically made by a single person or a committee (i.e.~the
editorial board) who had an expertise that covered the scope of the
journal. As science became more specialized, new journals would form to
support and provide a source of validation to the new specialty. The
growth in science in the mid 1900s resulted in a shift from journals
struggling to find sufficient numbers of manuscript to publish to having
too many manuscripts submitted. It has been argued that the widespread
adoption of decentralized peer-review was due to the increased
specialization and to deal with the large number of manuscript
submissions (15). Peer-review did not achieve widespread use at many
journals, including the \emph{Journal of Bacteriology}, until the 1940s
and 1950s. Thus the ``tradition'' of peer-review is only 70 years old.
Given the rapid advances in communication technology and even greater
specialization within microbiology, it is worth pondering whether the
current scientific publishing system and peer-review system, in
particular, need to continue to adapt with our science.

@@

First, a common concern is that if a researcher posts their work as a
preprint, it will be ``scooped'' by another researcher and the preprint
author will lose their ability to claim primacy or their ability to
publish the work in a journal. Considering the preprint is a citable
work with a DOI, it would, in fact, be the preprint author that scooped
the second. The use of preprints uncouples the communication of the
discovery from the relevance of the discovery, which will come later
based on peer-review, comments from other scientists at meetings or
online, and eventually citations. A growing number of scientific
societies and journals, including ASM view preprints as citable and as
having a legitimate claim to primacy (1, 16--18). Some scientists worry
that with such protection a researcher can make a claim without valid
data to support their claims (3). This is possible; however, it is also
the responsibility of the scientific community to utilize the
peer-review mechanisms that are available to comment on those preprints
pointing out methodological problems or to indicate that they are
speaking beyond the data.

@@

A third concern is what role preprints should have in assessing a
scientist's productivity. Clearly use of publication metrics as an
indicator of a scientist's productivity and impact is a contentious
topic without even discussing the role of preprints. Regardless, given
the propensity for researchers to list manuscripts as being ``in
preparation'' or ``in review'' on an application or curriculum vitae,
listing them instead as preprints that can be reviewed by a committee
would significantly enhance an application and a reviewer's ability to
judge the application. In fact, several funding agencies including the
Wellcome Trust and the UK Medical Research Council encouraging
fellowship applicants to include preprints in their materials;
meanwhile, the NIH is in the process of soliciting input from the
scientific community on their role in grant applications. Others are
mandating that researchers post preprints for all of their work prior to
submitting the work to a journal (19).

Beyond these concerns, preprints are also causing some to change their
publication goals. Some authors are explicitly stating that a preprint
will not be submitted to a journal (20). Although these authors may be a
minority of those who post preprints, such an approach may be attractive
to those who need to cite a report of a brief research communication, a
critique of another publication, or negative results. It is clear that
the adoption of preprints will challenge how scientists interact and
evaluate each other's work. There is great potential to empower
researchers by controlling when a citable piece of work is made public.

@@

Second, preprints have proven useful for rapidly correcting the
scientific literature. On February 9, 2015, \emph{Cell Systems} posted a
study by Afshinnekoo et al. online (21). The study collected and
analyzed metagenomic sequence data from the New York City subway system
and reported finding \emph{Yersinia pestis} and \emph{Bacillus
anthracis}. Because of the focus on these two bioterrorism agents, this
study generated a considerable amount of media attention. On April 25,
2015, Petit et al. (22) posted a preprint to Zenodo demonstrating that
there was no evidence for \emph{B. anthracis} in the dataset. On July
29, 2015, a critique was published by \emph{Cell Systems} along with a
response from the original authors offering a correction to their
manuscript (23, 24). A second anecdote of using preprints to aid in
post-publication peer-review surrounds the publishing of a draft
tardigrade genome in \emph{The Proceedings of the National Academy of
Sciences}. On November 23, 2015 a study by Boothby et al. (25) was first
published online. The authors claimed that 17.5\% of its genes came from
bacteria, archaea, fungi, plants, and viruses. Another group had been
analyzing sequence data from a parallel tardigrade genome sequencing
project and did not observe the same result. A week later, on December
1, 2015, the second group had posted a preprint comparing the two genome
sequences and demonstrating that the exciting claims of horizontal gene
transfer were really the product of contaminants (26); this analysis
would eventually be published online by the original journal on March
24, 2016 followed by a rebuttal by the original authors on May 31, 2016
(27, 28). Two other analyses of the original data were published in May
2016 and a third was posted as a preprint on February 2, 2016 (29--31).
These anecdotes underscore the value of having a rapid posting cycle to
correcting errors in the scientific literature and that results posted
to preprint servers were able to correct the record within weeks of the
initial publication while the traditional path took six months in both
cases. A final notable case where preprints have accelerated the
correction of the scientific record was a preprint posted by Bik et al.
reporting numerous cases of image manipulation in peer reviewed studies
(32). Their preprint was posted on April 20, 2016 and published in
\emph{mBio} on June 7, 2016 (33). Instead of using preprints to react to
published papers that have been through peer review, it would be
interesting to consider how the editorial process for these examples and
the infamous ``Arsenic Life'' paper (34) would have been different had
they initially been posted as preprints.

@@

Measuring the impact and significance of scientific research is
notoriously difficult. Using several metrics I sought to quantify the
effect that broadly defined microbiology-affiliated preprints have had
on the work of others. Using the download statistics associated with
each preprint, I found that the median number of times an abstract or
PDF had been accessed was 923 (IQR: 603 to 1445) and 303 (IQR: 167 to
568), respectively. These values represent two aspects of posting a
preprint. First, they reflect the number of times people were able to
access science before it was published. Second, they reflect the number
of times people were able to access a version of a manuscript that is
published behind a paywall. To obtain a measure of a preprint's ability
to garner attention and engage the public, I obtained the Altmetric
Attention Score for each preprint (\textbf{Figure 1B}). The Altmetric
Attention Score measures the number of times a preprint or paper is
mentioned in social media, traditional media, Wikipedia, policy
documents, and other sources (35). A higher score indicates that a
preprint received more attention. Microbiology-affiliated preprints have
had a median Altmetric Attention Score of 7.3 (IQR: 3.2 to 16.3) and
those of all preprints hosted at \emph{bioRxiv} have had a median score
of 7.0 (IQR: 3 to 15.6). For comparison, the median Altmetric Attention
Score for articles published in \emph{mBio} published since 2013 was 4.5
(IQR: 1.2 to 13.6). Of all scholarship tracked by Altmetric, the median
Altmetric Attention Score for preprints posted at \emph{bioRxiv} ranks
at the 86 percentile (IQR: 66 to 94. A more traditional and
controversial metric of impact has been the number of citations an
article receives. I obtained the number of citations for the published
versions of manuscripts that were initially posted as preprints. To
allow for a comparison to traditional journals, I considered the
citations for preprints published in 2014 and 2015 as aggregated by Web
of Science (\textbf{Figure 1C}). Among the preprints that were published
and could be found in the Web of Science database, the median number of
citations was 6.5 (IQR: 2-14; mean: 13.6). For comparison, for the
papers published in \emph{mBio} in 2014 and 2015, the median number of
citations was 5 (IQR: 2-9; mean: 6.7). Although it is impossible to
quantify the quality or impact of research with individual metrics, it
is clear that preprints and the publications that result from them are
broadly accepted by the microbiology community.

\textbf{\emph{Preprints from an author's perspective.}} Posting research
as a preprint gives an author great control over when their work is made
public. Under the traditional peer-review model, an author may need to
submit and revise their work multiple times to several journals over a
long period before it is finally published. In contrast, an author can
post the preprint at the start of the process for others to consume and
comment on as it works its way through the editorial process. A first
example illustrates the utility of preprints for improving access to
research and the quality of its reporting. In 2014, my research group
posted a preprint to \emph{PeerJ Preprints} describing a method of
sequencing 16S rRNA gene sequences using the Pacific Biosciences
sequencing platform (36). At the same time, they submitted the
manuscript for review at \emph{PeerJ}. While the manuscript was under
review, they received feedback from an academic scientist and from
scientists at Pacific Biosciences that the impact of the results could
be enhanced by using a recently released version of the sequencing
chemistry. Instead of ignoring this feedback and resubmitting the
manuscript to address the reviews, we generated new data and submitted
an updated preprint a year later with a simultaneous submission to
\emph{PeerJ} that incorporated the original reviews as well as the
feedback we received from the academic scientist and Pacific
Biosciences. It was eventually published by \emph{PeerJ} (37, 38). Since
2015, we have continued to post manuscripts as preprints at the same
time as we have submitted manuscripts. Although the feedback to other
manuscripts has not been as helpful as our initial experience, we were
able to sidestep lengthy review processes by immediately making our
results available; in one case our preprint was available 7 months ahead
of the final published version (39, 40). As a second example, this
manuscript was posted to \emph{bioRxiv} as a preprint on
\textbf{February 22, 2017}. I then solicited feedback on the manuscript
using social media. Two weeks later, I incorporated the comments and
posted a revised preprint and submitted the manuscript to \emph{mBio}.
During that time, the abstract was read \textbf{XXXX} times and the PDF
was accessed \textbf{XXXX} times. This process engaged \textbf{XXXX}
commenters on \emph{bioRxiv}, \textbf{XXXX} people on Twitter,
\textbf{XXXX} on Facebook, and \textbf{XXXX} via email. I received
useful feedback from \textbf{XXX} people. Compared to the two or three
scientists that typically review a manuscript, this experience engaged a
much larger and more diverse community than had I foregone the posting
of a preprint. Although there are concerns regarding the quality of the
science posted to a preprint server, I contend that responsible use of
preprints as a part of the scientific process can significantly enhance
the science.

\textbf{\emph{Preprints from a publisher's perspective.}} A lingering
question is what role traditional journals will have in disseminating
research if there is broad adoption of preprints. Edited peer-reviewed
journals offer and will continue to offer significant added value to a
publication. A scholarly publishing ecosystem in which preprints coexist
with journals will allow authors to gain value from the immediate
communication of their work associated with preprints and also benefit
from the peer-reviewed, professionally edited publication that
publishers can provide. The professional copyediting, layout, and
publicity that these publishers offer are also unique features of
traditional journals. An alternative perspective is that preprints will
eventually replace traditional journals. Certainly, this is a radical
perspective, but it does serve to motivate publishers to capture the
innovation opportunities offered by preprints. By adopting
preprint-friendly policies, journals can create an attractive
environment for authors. As discussed above, a growing number of
journals have created mechanisms for authors to directly submit
preprints to their journals. An example is offered by the ASM, which
earlier this year launched a new venture from \emph{mSphere}.
mSphereDirect is a publication track of the journal that capitalizes on
the opportunity offered to couple preprints with rigorous peer-review.
mSphereDirect. actively encourages authors to post their manuscripts as
preprints as part of an author-driven editorial process where an
editorial decision is rendered within five days and publication in
\emph{mSphere} within a month (41). ASM is developing a new platform,
MicroNow, which will help coalesce specific communities within the
microbial sciences, further enhancing the use of preprints as well as
published articles (Stefano Bertuzzi, personal communication). In
addition to integrating preprints into the traditional editorial
process, several professional societies have also explicitly supported
citation of preprints in their other publications and recognize the
priority of preprints in the literature (16--18). These are policies
that empower authors and make specific journals more attractive. Other
practices have great potential to improve the reputation of journals. As
measured above, preprints are able to garner attention on par with
papers published in highly selective microbiology journals. Thus, it is
in a journal's best interest to recruit these preprints to their
journals. Several journals including \emph{PLOS Genetics} and
\emph{Genome Biology} have publicly stated that they scout preprints for
this purpose (42, 43). Preprints can also be viewed as a lost
opportunity to journals. A preprint that garners significant attention
may be ignored when it is finally published, brining little additional
attention to the journal. Going forward, it will be interesting to see
the innovative approaches that publishers develop so that they can
benefit by incorporating preprints into their process and whether
publishers' influence is reduced by the widespread adoption of
preprints.

@@

\hyperdef{}{ref-Angell1991}{\label{ref-Angell1991}}
9. \textbf{Angell M}, \textbf{Kassirer JP}. 1991. The ingelfinger rule
revisited. New England Journal of Medicine \textbf{325}:1371--1373.
doi:\url{http://doi.org/10.1056/nejm199111073251910}.

\hyperdef{}{ref-ICMJE}{\label{ref-ICMJE}}
10. Recommendations for the conduct, reporting, editing, and publication
of scholarly work in medical journals.
\url{http://www.icmje.org/news-and-editorials/icmje-recommendations_annotated_dec16.pdf}.

\hyperdef{}{ref-PreprintPolicy}{\label{ref-PreprintPolicy}}
11. List of academic journals by preprint policy.
\url{https://en.wikipedia.org/wiki/List_of_academic_journals_by_preprint_policy}.

\hyperdef{}{ref-Sherpa}{\label{ref-Sherpa}}
12. Publisher copyright policies \& self-archiving.
\url{http://www.sherpa.ac.uk/romeo/index.php}.

\hyperdef{}{ref-Drubin2016}{\label{ref-Drubin2016}}
13. \textbf{Drubin DG}. 2016. The mismeasure of scientific research
articles and why MBoC quickly embraced preprints. Molecular Biology of
the Cell \textbf{27}:3181--3182.
doi:\url{http://doi.org/10.1091/mbc.e16-09-0651}.

\hyperdef{}{ref-Spier2002}{\label{ref-Spier2002}}
14. \textbf{Spier R}. 2002. The history of the peer-review process.
Trends in Biotechnology \textbf{20}:357--358.
doi:\url{http://doi.org/10.1016/s0167-7799(02)01985-6}.

\hyperdef{}{ref-Burnham1990}{\label{ref-Burnham1990}}
15. \textbf{Burnham JC}. 1990. The evolution of editorial peer review.
JAMA: The Journal of the American Medical Association \textbf{263}:1323.
doi:\url{http://doi.org/10.1001/jama.1990.03440100023003}.

\hyperdef{}{ref-Pulverer2016}{\label{ref-Pulverer2016}}
16. \textbf{Pulverer B}. 2016. Preparing for preprints. The EMBO Journal
\textbf{35}:2617--2619.
doi:\url{http://doi.org/10.15252/embj.201670030}.

\hyperdef{}{ref-Loew2016}{\label{ref-Loew2016}}
17. \textbf{Loew LM}. 2016. Peer review and bioRxiv. Biophysical Journal
\textbf{111}:E01--E02.
doi:\url{http://doi.org/10.1016/j.bpj.2016.06.035}.

\hyperdef{}{ref-Vale2016}{\label{ref-Vale2016}}
18. \textbf{Vale RD}, \textbf{Hyman AA}. 2016. Priority of discovery in
the life sciences. eLife \textbf{5}.
doi:\url{http://doi.org/10.7554/elife.16931}.

\hyperdef{}{ref-Dolgin2016}{\label{ref-Dolgin2016}}
19. \textbf{Dolgin E}. 2016. Big biology projects warm up to preprints.
Nature. doi:\url{http://doi.org/10.1038/nature.2016.21074}.

\hyperdef{}{ref-SinghChawla2017}{\label{ref-SinghChawla2017}}
20. \textbf{Chawla DS}. 2017. When a preprint becomes the final paper.
Nature. doi:\url{http://doi.org/10.1038/nature.2017.21333}.

\hyperdef{}{ref-Afshinnekoo2015a}{\label{ref-Afshinnekoo2015a}}
21. \textbf{Afshinnekoo E}, \textbf{Meydan C}, \textbf{Chowdhury S},
\textbf{Jaroudi D}, \textbf{Boyer C}, \textbf{Bernstein N},
\textbf{Maritz JM}, \textbf{Reeves D}, \textbf{Gandara J},
\textbf{Chhangawala S}, \textbf{Ahsanuddin S}, \textbf{Simmons A},
\textbf{Nessel T}, \textbf{Sundaresh B}, \textbf{Pereira E},
\textbf{Jorgensen E}, \textbf{Kolokotronis S-O}, \textbf{Kirchberger N},
\textbf{Garcia I}, \textbf{Gandara D}, \textbf{Dhanraj S},
\textbf{Nawrin T}, \textbf{Saletore Y}, \textbf{Alexander N},
\textbf{Vijay P}, \textbf{Hénaff EM}, \textbf{Zumbo P}, \textbf{Walsh
M}, \textbf{O'Mullan GD}, \textbf{Tighe S}, \textbf{Dudley JT},
\textbf{Dunaif A}, \textbf{Ennis S}, \textbf{O'Halloran E},
\textbf{Magalhaes TR}, \textbf{Boone B}, \textbf{Jones AL}, \textbf{Muth
TR}, \textbf{Paolantonio KS}, \textbf{Alter E}, \textbf{Schadt EE},
\textbf{Garbarino J}, \textbf{Prill RJ}, \textbf{Carlton JM},
\textbf{Levy S}, \textbf{Mason CE}. 2015. Geospatial resolution of human
and bacterial diversity with city-scale metagenomics. Cell Systems
\textbf{1}:72--87. doi:\url{http://doi.org/10.1016/j.cels.2015.01.001}.

\hyperdef{}{ref-Petit2015}{\label{ref-Petit2015}}
22. \textbf{Petit III RA}, \textbf{Ezewudo M}, \textbf{Joseph SJ},
\textbf{Read TD}. 2015. Searching for anthrax in the New York City
subway metagenome. doi:\url{http://doi.org/10.5281/zenodo.17158}.
